Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}

### 2018-05-06 Documents/M1/realizableFermionicM1/sections/algebraicClosures.tex
Modified Kershaw closure section.

The basic principle behind Kershaw closure is derived from the fact that $\cR$ is convex.
Due to the convexity, one can write any element in $\cR$ as a convex combination of the elements on the realization boundary. 
Therefore, Kershaw closure satisfies realizability inherently.
For fermionic radiation, the boundary is based on the Heaviside step functions.
Here we introduce a closure function $\Theta(x)$ given by Banach \& Larecki \cite{banachLarecki_2017a}:
\begin{equation}
  \Theta_{\mbox{\tiny K}}^{\mbox{\tiny BL}}(x)=x^{2}
\end{equation}

>>>>

The basic principle behind Kershaw closure is derived from the fact that the realizable set defined by $(\cJ, \vect{\cH}, \vect{K})$ is convex.
Due to the convexity, it's sufficient and necessary for an element in the convex set be expressed as a convex combination of two elements that on the set boundary.
The Kershaw closure assumes that the convex combination has a constant coefficient which is independent from $(\cJ, \vect{\cH})$.
Therefore, using the lower occupancy limit, one can determine the coefficient and apply the convex combination as an approximation.
Here we introduce a closure function $\Theta(x)$ given by Banach \& Larecki \cite{banachLarecki_2017a}:
\begin{equation}
  \Theta_{\mbox{\tiny K}}^{\mbox{\tiny BL}}(x)=x^{2}
\end{equation}
